\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-26 paper/ms.tex
ABC writing

\section{Approximate Bayesian Computation}
Nested Sampling can be used to solve ``Approximate Bayesian Computation''
problems elegantly and efficiently.

Approximate Bayesian Computation (ABC), also known as likelihood-free inference,
is a set of Monte Carlo techniques for approximating a posterior distribution
without having to evaluate the likelihood function $L(\theta)$.

. Instead, the ability to
generate simulated data sets from the sampling distribution is required.
Since a sampling distribution must be specified, it is not the assumption of
a specific likelihood that is avoided (indeed, a sampling distribution and
a data set imply a particular likelihood function), rather that we cannot
evaluate it cheaply as a function of $\params$ and $\data$.

All Bayesian updating conditions on the truth of a proposition. We sometimes
speak and use notation as if we're conditioning on the value of a variable, for
example by writing the posterior distribution as $p(\params | \data)$. However,
this is shorthand for $p(\params | \data = \dobs)$. In the prior state of
knowledge, the proposition $(\data = \dobs)$ could have been either true or
false, but in the posterior state of knowledge it is definitely true.
In the case of ``continuous data'' (really a continuous {\it space of
possibilities for the data before we learned it}) we're conditioning on a
proposition like $(\data \in [\dobs, \dobs+\epsilon])$ and implicitly
taking the limit $\epsilon \to 0$.

>>>>

\section{Approximate Bayesian Computation}
Nested Sampling can be used to solve Approximate Bayesian Computation (ABC)
problems elegantly and efficiently.
Also known (misleadingly) as likelihood-free inference,
ABC
is a set of Monte Carlo techniques for approximating the posterior distribution
without having to evaluate the likelihood function $L(\theta)$. Instead, 
the user must be able to cheaply
generate simulated data sets from the sampling distribution $p(D|\theta, I)$.
Since a sampling distribution must be specified, it is not that there is
no likelihood function (indeed, a sampling distribution and
a data set imply a particular likelihood function), rather that we cannot
evaluate it cheaply and therefore cannot use MCMC.

All Bayesian updating conditions on the truth of a proposition. We sometimes
speak and use notation as if we're conditioning on the value of a variable, for
example by writing the posterior distribution as
$p(\theta | D, I)$. However,
this is shorthand for $p(\theta | D = D_{\rm observed}, I)$, and
$D = D_{\rm observed}$ is a statement that could have been either
true or false in the prior state of knowledge, and is known to be true
in the posterior state of knowledge.
In the case of ``continuous data'' (really a continuous {\it space of
possibilities for the data before we learned it}) we're conditioning on a
proposition like $(D \in \mathcal{R})$ where $\mathcal{R}$ is a region, and
then implicitly taking a limit as the size of $\mathcal{R}$ goes to zero.

ABC works by replacing the proposition $D = D_{\rm observed}$ with a logically
weaker one.
